Risk Perceptions for Wearable Devices

### 2015-01-08 wearables_survey.tex
Finish my pass through the related work section.

\subsection{User Perceptions and Behaviors}
{\color{red} this section is still rough! David will redo.} 
One limitation of user perceptions is that people don't always have enough information to make privacy-sensitive decisions; even if they do, they often trade off long-term privacy for short-term benefits ~\cite{acquisti2005privacy}. Actual behavior deviates from self-reported behaviors ~\cite{jensen2005privacy} and privacy preferences ~\cite{spiekermann2001privacy}.

>>>>

\subsection{User Perceptions and Behaviors}
In this paper we focus on measuring people's perceptions of security and privacy risks.
One limitation of user perceptions is that people don't always have enough information to make privacy-sensitive decisions; even if they do, they often trade off long-term privacy for short-term benefits~\cite{acquisti2005privacy}. Also, actual behavior may deviate from self-reported behaviors~\cite{jensen2005privacy} and privacy preferences~\cite{spiekermann2001privacy}.
